---
title: "04_AMG_Bar_Graph"
output: html_document
author: "Ema H Graham"
---
For Questions Email: ema.graham@huskers.unl.edu

## Description

Input Notes: 
Will need the following files:
- VIBRANT_AMG_pathways_ALL_unmapped_1000_contigs.tsv (generated using VIBRANT; is found in VIBRANT_results file)

Output Notes: 
Will generate metabolism pathway bar graph showing prevalence of AMG metabolism pathway types found in phage population (Figure 3A)

```{r setup,message=FALSE}
library(ggthemes)
library(ggplot2)
library(readr)
library(ggsci)
library(cowplot)
```

# Generate metabolism pathway bar graph

Obtain metabolism pathway data from the output of VIBRANT (produced using 02_Identify_Phage.sh)
```{r,message=FALSE,warning=FALSE,results="hide"}
VIBRANT_AMG_pathways_unmapped_contigs <- read_delim("VIBRANT_results_ALL_unmapped_1000_contigs/VIBRANT_AMG_pathways_ALL_unmapped_1000_contigs.tsv", 
    "\t", escape_double = FALSE, trim_ws = TRUE)
```
Order contigs by Metabolism type
```{r,message=FALSE,warning=FALSE,results="hide"}
VIBRANT_AMG_pathways_unmapped_contigs <- VIBRANT_AMG_pathways_unmapped_contigs[order(VIBRANT_AMG_pathways_unmapped_contigs$Metabolism),]
```
Turn your 'Pathway' column into a character vector
```{r,message=FALSE,warning=FALSE,results="hide"}
VIBRANT_AMG_pathways_unmapped_contigs$Pathway <- as.character(VIBRANT_AMG_pathways_unmapped_contigs$Pathway)
```
Then turn it back into a factor with the levels in the correct order
```{r,message=FALSE,warning=FALSE,results="hide"}
VIBRANT_AMG_pathways_unmapped_contigs$Pathway <- factor(VIBRANT_AMG_pathways_unmapped_contigs$Pathway, levels=unique(VIBRANT_AMG_pathways_unmapped_contigs$Pathway))
````
Make pathway barplot using ggplot
```{r,message=FALSE,warning=FALSE,results="hide"}
amg_barg<-ggplot(data=VIBRANT_AMG_pathways_unmapped_contigs, aes(x=Pathway, y=Total_AMGs, fill=Metabolism)) +
  geom_bar(position = "dodge", stat="identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust=1, size = 10),plot.title = element_blank())+ 
  ylab("Total AMGs")+
  theme(panel.background = element_blank())+
  theme(plot.title = element_text(face = "bold",
                                         size = rel(1.2), hjust = 0.5))+
  theme(axis.text = element_text(colour="black"), 
               axis.line = element_line(colour="black"),
               axis.ticks = element_line())+
    scale_y_continuous(
    # don't expand y scale at the lower end
    expand = expansion(mult = c(0, 0.05))
  )
          
plot_pathway<-amg_barg + coord_flip()
#Save plot as "pathway.pdf"
ggsave(plot=plot_pathway,"pathway.pdf",dpi = 600, pointsize=10, height = 40, width= 35, units = "cm")
```
This will generate bar plot with the breakdown of pathways and metabolism types as seen in Figure 3A.
Bar plot was then edited in Adobe Illustrator to combine it with figures 3B and 3C.
Alternative ploting idea: might want to break up into one overall and then have seperate graphs for each metabolism type.
